### 2017-01-28 manuscript.rmd
fixed Hominini node names

	# These clade dates are from the KMRR code, they got them from http://timetree.org/
	calibration_times = data.frame(
		age.min =
			c(  8, 29, 92, 162, 167, 296 ), 
		clade = 
			c( "Homininae", "Catarrhini", "Euarchontoglires", "Theria", "Mammalia", "Amniota" ),
		stringsAsFactors=FALSE
	)
```

@@

@@

>>>>

	# These clade dates are from the KMRR code, they got them from http://timetree.org/
	calibration_times = data.frame(
		age.min =
			c(  7, 9, 29, 92, 162, 167, 296 ), 
		clade = 
			c( "Hominini", "Homininae", "Catarrhini", "Euarchontoglires", "Theria", "Mammalia", "Amniota" ),
		stringsAsFactors=FALSE
	)
```

@@

	#' Fix ensembl clade names.
	#' Homininae is pan + homo + gorilla
	#' Hominini is pan + homo
	#' ENSEMBL Compara trees lislabel Hominini as Homininae
	#' 
	#' @param nhx A phylogenetic tree as a treeio::treedata object
	#' @return A phylogenetic tree as a treeio::treedata object
	#' @export
	fix_hominini = function( nhx ) {
		# Get the numbers for all nodes labeled as homininae
		homininae_nodes = nhx@data$node[ nhx@data$label == "Homininae" ]

		# Check which have no gorilla as a descendent
		no_gorilla = sapply(
			homininae_nodes,
			function( x ){
				tips = hutan::tip_descendants( nhx@phylo, x )
				tip_species = nhx@data$species[ tips ]
				return( ! "gorilla_gorilla" %in% tip_species )
			}
		)

		if( any( no_gorilla ) ){
			hominini_nodes = homininae_nodes[ no_gorilla ]
			nhx@data$label[ hominini_nodes ] = "Hominini"
		}

@@

	# fix clade names
	gene_trees_pruned = lapply( gene_trees_pruned, fix_hominini )
